Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
fixed GitHub capitalization

In past studies, both technical factors and social factors have been found to be
important when predicting pull request success~\cite{tsay14icse,tsay14fse}.
In this study we are interested in analyzing the quality of a contribution 
at a lower granulairity level, commit level. We will analyze this in the 
context of continuous integration, using some of the social attributes provided
by Github as a proxy for the developer's experience level and familiarity with
the process, and their importance when grouped with technical attributes of the commit as 
confounds for the complexity of the commit being pushed.

@@

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor torwards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis
CI jobs.\footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in Github and its correlation with software 
quality. Unlike the works previously listed, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

@@

\textbf{Do social attributes, gathered 
from the Github profiles of developers,
allow for more accurate predictions than only using technical data?}

@@

We evaluated the predictive power of the social factors using a decision
tree~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold cross 
validation with the data in each data set.
To give an answer to main research question: ``Do social attributes, gathered 
from the Github profiles of developers,
allow for more accurate predictions than only using technical data?", we 
present the following results:

@@

\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
 projects used in this dataset have also been filtered to be popular (having more 
 than 10 watches on Github), and to have a history of using the continuous 
 integration tool Travis CI for more than 50 builds. All these features help to 
 build the notion that since we are building our analysis on top of a vast 
 dataset comprehending a wide diversity of projects, the threat of this analysis 
 not generalizing to other projects is mitigated.

>>>>

In past studies, both technical factors and social factors have been found to be
important when predicting pull request success~\cite{tsay14icse,tsay14fse}.
In this study we are interested in analyzing the quality of a contribution 
at a lower granulairity level, commit level. We will analyze this in the 
context of continuous integration, using some of the social attributes provided
by GitHub as a proxy for the developer's experience level and familiarity with
the process, and their importance when grouped with technical attributes of the commit as 
confounds for the complexity of the commit being pushed.

@@

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor torwards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis
CI jobs.\footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

@@

\textbf{Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?}

@@

We evaluated the predictive power of the social factors using a decision
tree~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold cross 
validation with the data in each data set.
To give an answer to main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?", we 
present the following results:

@@

\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
 projects used in this dataset have also been filtered to be popular (having more 
 than 10 watches on GitHub), and to have a history of using the continuous 
 integration tool Travis CI for more than 50 builds. All these features help to 
 build the notion that since we are building our analysis on top of a vast 
 dataset comprehending a wide diversity of projects, the threat of this analysis 
 not generalizing to other projects is mitigated.
